Algorithm explanation

### 2013-04-20 article/algo.tex
Fix for consistency on symbols

Given an acyclic Horn graph (or called a Horn DAG), we define the
relation $u <^+ v$ as follows.
\[ u <^+ v \Longleftrightarrow \exists \theta. (u,v,\theta) \in E \]
By the assumption that $G$ is acyclic, $<^+$ is a well-founded
relation. We assume without loss of generality that $V$ contains the
least element $v_\bot$ with respect to $<^+$; otherwise we can always
ignore $v_\bot$ with $\varphi(v_\bot) = 0 \leq -1$.

For each $v \in V$, we define $\Delta(v) = (a_v x \leq b_v, C_v)$,
where
\begin{itemize}
\item $a_v x \leq b_v$ is a linear inequality that may contain
  coefficient variables
\item $C_v$ is a set of linear expressions on coefficient variables.
\end{itemize}
Intuitively, the pair $(\mathbf{a} \mathbf{x} \leq b, C)$ denotes the
set of inequalities:

@@

Given $\varphi(v_\bot) = \mathbf{a}_0 \mathbf{x} \leq b_0$, any
solution $\sigma$ to the constraint $C_\star = C_{v_\bot} \cup {
  \mathbf{a}_0 = \mathbf{a}_{v_\bot} } \cup { b_0 = b_{v_\bot} }$
gives a simple solution for $G$ if $C_\star$ is satisfiable, i.e., we
should have:

\begin{quote}
If $\models \sigma(C_\star)$, then $\rho$ defined by
\begin{align*}
 \rho = \left\lbrace
  \left( P, \sigma(\mathbf{a}_v \mathbf{x} \leq b_v) \right) \middle|
  \forall v \in V. \varphi(v) = P(\mathbf{x})
 \right\rbrace
\end{align*}
is a solution of $G$.
\end{quote}

If $C_\star$ is unsatisfiable, there are two possibility for them.

>>>>

Given an acyclic Horn graph (or called a Horn DAG), we define the
relation $u <^+ v$ as follows.
\[ u <^+ v \Longleftrightarrow \exists \theta. (u,v,\theta) \in E \]
By the assumption that $G$ is acyclic, $<^+$ is a well-founded
relation. We assume without loss of generality that $V$ contains the
least element $v_\bot$ with respect to $<^+$; otherwise we can always
implicitly assume $\varphi(v_\bot) = 0 \leq -1$.

For each $v \in V$, we define
$\Delta(v) = (\mathbf{a}_v \mathbf{x} \leq b_v, C_v)$
, where
\begin{itemize}
\item $\mathbf{a}_v \mathbf{x} \leq b_v$ is a linear inequality that
  may contain coefficient variables
\item $C_v$ is a set of linear expressions on coefficient variables.
\end{itemize}
Intuitively, the pair $(\mathbf{a} \mathbf{x} \leq b, C)$ denotes the
set of inequalities:

@@

Given a set of maximal nodes
$V_\top = \left\lbrace v \in V \middle| \neg(\exists v'. v <^+ v') \right\rbrace$,
any model $\sigma$ to the constraint
$C_{V_\top} = \bigwedge_{v \in V_{\top}} C_v$ gives a
simple solution for $G$ if $C_{V_\top}$ is satisfiable, i.e., we
should have:

\begin{quote}
If $\models \sigma(C_{V_\top})$, then $\rho$ defined by
\begin{align*}
 \rho = \left\lbrace
  \left( P, \sigma(\mathbf{a}_v \mathbf{x} \leq b_v) \right) \middle|
  \forall v \in V. \varphi(v) = P(\mathbf{x})
 \right\rbrace
\end{align*}
is a solution of $G$.
\end{quote}

If $C_{V_\top}$ is unsatisfiable, there are two possibilities for them.
